Developing Software Center Using Evolutionary Prototyping Based-on HTML5

### 2014-05-04 Latex/Paper_format.tex
kurang pengujian ma squence diagram

\begin{abstract}
%\boldmath
The abstract goes here.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

HTML5 is a trend of programming because this technology easy to adapted, can run in many platforms up to desktop utilization [2]. Manokwari Desktop a desktop environment for BlankOn Linux is base on HTML5 and GNOME 3. Development software center base on HTML5 can run consistent with development of BlankOn Linux [3]. This research tries to make software center HMTL5-based as solution for BlankOn Linux.

@@

YaST (Yet another Setup Tool)
Software center for openSUSE. It use to manage all of user need for use openSUSE. Example to install application, package, network setting etc. YaST use ruby and YCP for language programming and Qt for user interface[3].

Ubuntu Software Center
Software management for Ubuntu by Canonical. It is free software written in Python, PyGTK/PyGObject based on GTK+ and the further development of the GNOME application, gnome-app-install.[4][5]

@@

WebKit is also used as the basis for the experimental browser included with the Amazon Kindle e-book reader, as well as the default browser in the Apple iOS, Android, BlackBerry 10, and Tizen mobile operating systems. WebKit's C++ application programming interface provides a set of classes to display web content in windows, and implements browser features such as following links when clicked by the user, managing a back-forward list, and managing a history of pages recently visited.[6] bart

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{image/webkit.png}
\caption{How Webkit Work}
\end{figure}

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{image/webkitcomponents.png}
\caption{Webkit Major Components}
\end{figure}

WebKitGTK+ is the GNOME platform port of the WebKit rendering engine. Offering WebKit’s full functionality through a set of GObject-based APIs, it is suitable for projects requiring any kind of web integration, from hybrid HTML/CSS applications to full-fledged web browsers, like Epiphany and Midori. It’s useful in a wide range of systems from desktop computers to embedded systems like phones, tablets, and televisions. WebKitGTK+ is made by a lively community of developers and designers, who hope to bring the web platform to everyone.[7] webkitgtk.org

\subsection{WarSi}
WarSi (Warung aplikasi) is the name of software center run in BlankOn Linux. It job to help user management applications by make Graphic User Interface. To do management WarSi need link to apt. its use vala programming. Object oriented programming base on c and GObject.

Valac, the Vala compiler, is a self-hosting compiler that translates Vala source code into C source and header files. It uses the GObject type system to create classes and interfaces declared in the Vala source code. The syntax of Vala is similar to C\#, modified to better fit the GObject type system. Vala supports modern language features as the following:

\begin{itemize}
\item Interfaces
\item Properties
\item Signals
\item Foreach
\item Lambda expressions
\item Type inference for local variables
\end{itemize}

Vala is designed to allow access to existing C libraries, especially GObject-based libraries, without the need for runtime bindings. All that is needed to use a library with Vala is an API file, containing the class and method declarations in Vala syntax. Vala currently comes with experimental bindings for GLib and GTK+. It's planned to provide generated bindings for the full GNOME Platform at a later stage.

\section{Development WarSi}
\subsection{Design System}
Figure 3 show how design of WarSi.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{image/DesignSystem.png}
\caption{Design System}
\end{figure}

\subsection{Development Method}
System development methods used in this study is the method of Evolutionary Prototyping. Evolutionary prototyping method has the steps as shown in Figure 4.

@@

Evolutionary prototyping provides other benefits including:
\begin{itemize}
\item the clarification of management and user requirements;
\item the ability to uncover missing or previously unknown requirements;
\item the flexibility to meet changing constraints for software systems;
\item the provision of a method whereby users, management, and developers can communicate about systems;
\item the easing of maintenance tasks;
\item the creation of ‘better’ user interfaces;
\item prototyping with quality; and
\item the ability for developers to reflect on lessons learned during system development.
\end{itemize}

Steps of Evolutionary Prototyping:
\subsubsection{Initial Concept and Requirement}

\subsubsection{Quick Design}

\subsubsection{Build Prototype}

\subsubsection{Costumer Evaluation, Update}

\subsubsection{If not done yet, Refine design and prototype}

\subsubsection{If happy, final testing and product release}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.7]{image/Usecase.png}
\caption{Use case Diagram}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.7]{image/ActivityDiagram.png}
\caption{Activity Diagram}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{image/ADSearchApp.png}
\caption{Activity Diagram Search Application}
\end{figure}

Figure 7 is an activity diagram for a search application. Search Application is divided into two, namely by entering a keyword in the search field and the search for applications by category. Process for Figure 6 are:

\begin{itemize}
\item Users select search for applications by name or by category of applications,
\item If you select by name, users enter a keyword or the name of the application you are looking for in the search field to find the application,
\item If you select a category based application, the user selects a category that existed until the application is found,
\item Application is found, the user chooses to install/remove or update the application,
\item Installation process, and the process is complete.
\end{itemize}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{image/ADManagement.png}
\caption{Activity Diagram Repository Management}
\end{figure}

@@

\subsection{Result Development}
diisini apa ini?

\subsection{Testing}
Black box testing (also called functional testing) is testing that ignores the internal mechanism of a system or component and focuses solely on the outputs generated in response to selected inputs and execution conditions.[11]

@@

% use section* for acknowledgement
\section*{Acknowledgment}
Thank you to Ahmad Dahlan University for funding this research

@@

\bibitem{IEEEhowto:kopka}
Duncan Mac-Vicar P., \emph{What you should know about YaST}, Novell, Inc, 2008.

\bibitem{IEEEhowto:kopka}
Mathew Paul Thomas, \emph{Ubuntu Software Center}, http://wiki.ubuntu.com/SoftwareCenter.

\bibitem{IEEEhowto:kopka}
Lounpad Ubuntu

\bibitem{IEEEhowto:kopka}
Wiki BlankOn,

\bibitem{IEEEhowto:kopka}
John Dooley, \emph{Software Development and Professional Practice}, Springer Science Business Media, Inc, 2011.

\bibitem{IEEEhowto:kopka}
Carter, Ryan A.,Antón, Annie I.,Dagnino, Aldo., Williams, Laurie, \emph{Evolving Beyond Requirements Creep:A Risk-Based Evolutionary Prototyping Model}, North Carolina State University, 2001.

\bibitem{IEEEhowto:kopka}
IEEE, \emph{IEEE Standard 610.12-1990, IEEE Standard Glossary of Software Engineering Terminology}, 1990.

>>>>

\begin{abstract}
%\boldmath
The Software Center is a required application in all operating system, both conventional or mobile devices. BlankOn as the local operating system should have this application but in reality this application is not yet available. HTML5 is a trend of programming because this technology easy to adapted for desktop utilization. This research tries to make software center HMTL5-based as solution for BlankOn. System development methods used in this study is evolutionary prototyping. It possible to develop application base on prototype of software. Next step is implement prototype to language programming. Every progress will be correction to get better features. Progress will be finished if prototype had all features what needs. Stages of research is divided into several steps. first analysis similar applications, second design system, third implementation and testing of the system. Based on the results of functionality testing software center, the percentage obtained 100\% agree the system can run well. From the results usability testing software center, it is concluded that the respondents strongly agreed that as much as 80\% and 20\% agree. It can be concluded that the software center application can run well and smoothly.

\emph{Keywords : Vala; Webkit; HTML5; Software Center; BlankOn}
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

HTML5 is a trend of programming because this technology easy to adapted, can run in many platforms up to desktop utilization. Manokwari Desktop a desktop environment for BlankOn Linux is base on HTML5 and GNOME 3. Development software center base on HTML5 can run consistent with development of BlankOn Linux [1]. This research tries to make software center HMTL5-based as solution for BlankOn Linux.

@@

YaST (Yet another Setup Tool)
Software center for openSUSE. It use to manage all of user need for use openSUSE. Example to install application, package, network setting etc. YaST use ruby and YCP for language programming and Qt for user interface[2].

Ubuntu Software Center\\Software management for Ubuntu by Canonical. It is free software written in Python, PyGTK/PyGObject based on GTK+ and the further development of the GNOME application, gnome-app-install.[3][4]

@@

WebKit is also used as the basis for the experimental browser included with the Amazon Kindle e-book reader, as well as the default browser in the Apple iOS, Android, BlackBerry 10, and Tizen mobile operating systems. WebKit's C++ application programming interface provides a set of classes to display web content in windows, and implements browser features such as following links when clicked by the user, managing a back-forward list, and managing a history of pages recently visited [5].

\begin{figure}[!t]
\centering
\includegraphics[scale=0.5]{image/webkit.png}
\caption{How Webkit Work}
\end{figure}

\begin{figure}[!t]
\centering
\includegraphics[scale=0.5]{image/webkitcomponents.png}
\caption{Webkit Major Components}
\end{figure}

WebKitGTK+ is the GNOME platform port of the WebKit rendering engine. Offering WebKit’s full functionality through a set of GObject-based APIs, it is suitable for projects requiring any kind of web integration, from hybrid HTML/CSS applications to full-fledged web browsers, like Epiphany and Midori. It’s useful in a wide range of systems from desktop computers to embedded systems like phones, tablets, and televisions. WebKitGTK+ is made by a lively community of developers and designers, who hope to bring the web platform to everyone [6].

\subsection{WarSi (Software Center)}
WarSi (Warung aplikasi) is the name of software center run in BlankOn Linux. It job to help user management applications by make Graphic User Interface. To do management WarSi need link to apt. its use vala programming. Object oriented programming base on c and GObject.

Valac, the Vala compiler, is a self-hosting compiler that translates Vala source code into C source and header files. It uses the GObject type system to create classes and interfaces declared in the Vala source code. The syntax of Vala is similar to C\#, modified to better fit the GObject type system. Vala supports modern language features as the following: Interfaces; Properties; Signals; Foreach; Lambda; expressions; Type inference for local variables [7].

Vala is designed to allow access to existing C libraries, especially GObject-based libraries, without the need for runtime bindings. All that is needed to use a library with Vala is an API file, containing the class and method declarations in Vala syntax. Vala currently comes with experimental bindings for GLib and GTK+ It's planned to provide generated bindings for the full GNOME Platform at a later stage.

\section{Development WarSi}
\subsection{Design System}

WarSi design base on HTML5, AngularJS for front-end. Back-end use Vala programming. Vala chosen because it can communicate with operating system like run specific apt command use Vala API. Another reason Vala can run simultanly with Manokwari Desktop base on GNOME 3.

Figure 3 show how design of WarSi.

\begin{figure}[!t]
\centering
\includegraphics[scale=0.5]{image/DesignSystem.png}
\caption{Design System}
\end{figure}

\subsection{Development Method}
System development methods used in this study is the method of Evolutionary Prototyping. Evolutionary prototyping method has the steps as shown in Figure 4 [8].

@@

Evolutionary prototyping provides other benefits including[9]: the clarification of management and user requirements; the ability to uncover missing or previously unknown requirements; the flexibility to meet changing constraints for software systems; the provision of a method whereby users, management, and developers can communicate about systems; the easing of maintenance tasks; the creation of ‘better’ user interfaces; prototyping with quality; and the ability for developers to reflect on lessons learned during system development.

Steps of Evolutionary Prototyping:
\subsubsection{Initial Concept and Requirement}
At this stage will be determined what will be in software center includes system requirements,  criteria, the function to be achieved. This stage is important that detailed description of the application can be explained from the beginning.

\subsubsection{Quick Design}
The stage design is done in standard applications with minimal functionality to answer the important points that have been described in the previous step. Design prototype mock-up done in the form of the initial design and the functions that can run applications.

\subsubsection{Build Prototype}
From the results of the initial prototype design to be started in the form of program code. Starting from the design of the interface using HTML5, CSS3, javascript. The design is achieved not have to be exactly the same as designed. The next thing is to combine the Vala programming, Webkit as the back-end Software Center. Installation of container is done at this stage that some of the functions of the application can run. After this initial prototype Software Center obtained. This process also includes whether the application can be run
in BlankOn Linux.

\subsubsection{Costumer Evaluation, Update}
Prototype has been done early discussion back to the client for review and evaluate, both design, functional, and usability. Any corrections and recommendation will be collected.

\subsubsection{If not done yet, Refine design and prototype}
If client not satisfied, prototype must be correction base on recommendation which have been collect in previously.

\subsubsection{If happy, final testing and product release}
Once the prototype is approved client, the application entered the stage of release and make documentation of software center.

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.42]{image/Usecase.png}
\caption{Use case Diagram}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.7]{image/ActivityDiagram.png}
\caption{Activity Diagram}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.5]{image/ADSearchApp.png}
\caption{Activity Diagram Search Application}
\end{figure}

Figure 7 is an activity diagram for a search application. Search Application is divided into two, namely by entering a keyword in the search field and the search for applications by category. Process for Figure 6 are:
\begin{itemize}
\item Users select search for applications by name or by category of applications,
\item If you select by name, users enter a keyword or the name of the application you are looking for in the search field to find the application,
\item If you select a category based application, the user selects a category that existed until the application is found,
\item Application is found, the user chooses to install/remove or update the application,
\item Installation process, and the process is complete.
\end{itemize}

@@

\begin{figure}[!t]
\centering
\includegraphics[scale=0.5]{image/ADManagement.png}
\caption{Activity Diagram Repository Management}
\end{figure}

@@

\subsection{Result Development}
After development finished, the result is prototype software center for BlankOn Linux. Base on HTML5 for front-end. Screenshoot WarSi can be found in Figure 10 and Figure 11.

Figure 10 show page to search application.
\begin{figure}[!t]
\centering
\includegraphics[scale=0.31]{image/03HamalanPencarian.png}
\caption{Implement Search Page}
\end{figure}

Figure 11 show page repository management.
\begin{figure}[!t]
\centering
\includegraphics[scale=0.31]{image/02HalamanRepository.png}
\caption{Implement Repository Management}
\end{figure}

\subsection{Testing}
Black box testing (also called functional testing) is testing that ignores the internal mechanism of a system or component and focuses solely on the outputs generated in response to selected inputs and execution conditions.[10]

@@

% use section* for acknowledgement
% \section*{Acknowledgment}
% Thank you to Ahmad Dahlan University for funding this research

@@

\bibitem{IEEEhowto:manokwari}
\emph{Manokwari, Desktop shell for GNOME 3 with Gtk+ and HTML5 frontend} available at http://manokwari.blankonlinux.or.id/

\bibitem{IEEEhowto:mac-vicar}
Duncan Mac-Vicar P., \emph{What you should know about YaST}, Novell, Inc, 2008.

\bibitem{IEEEhowto:paul thomas}
Mathew Paul Thomas, \emph{Ubuntu Software Center}, http://wiki.ubuntu.com/SoftwareCenter, 2005.

\bibitem{IEEEhowto:ubuntu}
\emph{Ubuntu Software Center} available at https://launchpad.net/software-center

\bibitem{IEEEhowto:webkit}
Adam Bart, \emph{How WebKit Works}, webkit.org, 2010.

\bibitem{IEEEhowto:webkitgtk}
\emph{WebkitGTK+} available at http://webkitgtk.org/

\bibitem{IEEEhowto:vala}
Muhammad Anwari, \emph{GNOME 3 Application Development Beginner}, Birmingham: Packt Publishing Ltd, 2013.

\bibitem{IEEEhowto:dooley}
John Dooley, \emph{Software Development and Professional Practice}, Springer Science Business Media, Inc, 2011.

\bibitem{IEEEhowto:ryan}
Ryan A. Carter, Annie I. Antón, Aldo Dagnino, Laurie Williams, \emph{Evolving Beyond Requirements Creep:A Risk-Based Evolutionary Prototyping Model}, North Carolina State University, 2001.

\bibitem{IEEEhowto:IEEE}
IEEE, \emph{IEEE Standard 610.12-1990, IEEE Standard Glossary of Software Engineering Terminology}, 1990.

\bibitem{IEEEhowto:IEEE}
Laurie Williams, \emph{Testing Overview and Black-Box Testing Techniques}, 2006
